Paper Figures and Text

### 2022-11-24 Fish Data Analysis/Paper_Figures.qmd
Working on velocity cor graphs

velocity_cor_data <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,2))) %>% filter(round_Distance != 8)

velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,2))) %>%
                                               filter(Flow == "Still Water") %>%
                                               group_by(round_Distance,Flow_Ablation_Darkness) %>%
                                               summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
                                                         sd_Speed_Diff = sd(abs(Speed_Diff))) %>%
                                               ungroup()
```

```{r}
ggplot(velocity_cor_data, aes(x = Distance, y = Spatial_Auto))+
  geom_point(alpha = 0.1)+
  theme_classic()+ 
  theme(legend.position = "none") +
  ylab("Correlation Strength")+
  xlab("Distance (BL)")
```

>>>>

velocity_cor_data <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,1))) %>% filter(round_Distance != 8)

velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,2))) %>%
                                               filter(Flow == "Still Water") %>%
                                               group_by(round_Distance,Flow_Ablation_Darkness) %>%
                                               summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
                                                         sd_Speed_Diff = sd(abs(Speed_Diff)),
                                                         mean_Spatial_Auto = mean(abs(Spatial_Auto)),
                                                         sd_Spatial_Auto = sd(abs(Spatial_Auto))) %>%
                                               ungroup()
```

```{r}
ggplot(velocity_cor_data, aes(x = Distance, y = Spatial_Auto))+
  geom_point(alpha = 0.1)+
  theme_classic()+ 
  theme(legend.position = "none") +
  ylab("Correlation Strength")+
  xlab("Distance (BL)")

ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Spatial_Auto, color = Flow_Ablation_Darkness))+
  geom_point(position=position_dodge(width = 0.6))+
  geom_errorbar(aes(ymin = mean_Spatial_Auto-sd_Spatial_Auto, ymax = mean_Spatial_Auto+sd_Spatial_Auto),
                position=position_dodge(width = 0.6))+
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  theme_classic()
```
